### 2021-02-15 Modules/sec_prlm_timeSpaceSig.tex
rev03

As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken the same time $t$.
A basic application of the sensor array is the beamformer, designed to enhance signals from certain directions while suppressing other signals from unwanted directions, forming a beam directed to the enhanced direction.  
\begin{figure}[ht!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
        \put(20,65){\rotatebox{-50}{\tiny{Impinging wavefront}}}
        \put(49,33.25){\rotatebox{0}{$\theta$}}
        \put(15,25){\rotatebox{0}{\tiny{0}}}
        \put(28,25){\rotatebox{0}{\tiny{1}}}
        \put(41,25){\rotatebox{0}{\tiny{2}}}
        \put(80,25){\rotatebox{0}{\tiny{$N-1$}}}
        \put(16,20){\rotatebox{0}{\tiny{$\omega_{0}$}}}
        \put(29.5,20){\rotatebox{0}{\tiny{$\omega_{1}$}}}
        \put(42,20){\rotatebox{0}{\tiny{$\omega_{2}$}}}
        \put(81,20){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
        \put(50.5,3.5){\rotatebox{0}{\tiny{$z\rBrace{t}$}}}
        \end{overpic}
    \end{center}
     \caption{ULA based coherent processing of simultaneous spatially sampled signal, measuring a wavefront impinging from DOA $\theta$}
    \label{fig_ULA_imping}
\end{figure}
In complimentary to Fig.~\ref{fig_ULA_sketch}, Fig.~\ref{fig_ULA_imping} adds the processor layer of the beamformer.
\par A temporal snapshot measured by the array at time $t$ is
\begin{equation}
\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T},
\end{equation}
where $p_{n}$ denotes the $n$-th sensor position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
Considering the \emph{conventional beamformer} \cite{van2004optimum}, the output ($y\rBrace{t}$) is expressed by:
\begin{equation}
z\rBrace{t} = \sum_{n=0}^{N-1}{f\rBrace{t,p_{n}}\omega_{n}^{*}},
\end{equation}
where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at angular frequency $w$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
The wave signals spatially sampled by the sensor array inputs are
\begin{equation}
\label{eq_prlm_timeSpace_outputVec}
\vecnot{f}\rBrace{t,x} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
\end{equation}
where $\tau = \frac{d\cdot{}\cos{\theta}}{c}$ is the propagation delay between consecutive sensors and $c$ is the wave's velocity in the medium.
Considering narrowband signals (i.e. $s\rBrace{t}=\exp^{-j\omega{}t}$), the time delay $\tau$ translates to a mere phase shift and an auxiliary dephased \emph{steering vector} takes the form of
\begin{equation}
\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\rBrace{N-1}\omega\tau}}^{T}.
\end{equation}
As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal sub space in the noiseless scenario.

>>>>

As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken the same time $t$.
A basic application of the sensor array is the beamformer, designed to enhance signals from certain directions while suppressing other signals from unwanted directions, forming a beam directed to the enhanced direction.  
\begin{figure}[ht!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        %grid, 
        tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
        \put(20,65){\rotatebox{-50}{\tiny{Impinging wavefront}}}
        \put(49,33.25){\rotatebox{0}{$\theta$}}
        \put(15,25){\rotatebox{0}{\tiny{0}}}
        \put(28,25){\rotatebox{0}{\tiny{1}}}
        \put(41,25){\rotatebox{0}{\tiny{2}}}
        \put(80,25){\rotatebox{0}{\tiny{$N-1$}}}
        \put(16,20){\rotatebox{0}{\tiny{$\omega_{0}$}}}
        \put(29.5,20){\rotatebox{0}{\tiny{$\omega_{1}$}}}
        \put(42,20){\rotatebox{0}{\tiny{$\omega_{2}$}}}
        \put(81,20){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
        \put(50.5,3.5){\rotatebox{0}{\tiny{$z\rBrace{t}$}}}
        \end{overpic}
    \end{center}
     \caption{ULA based coherent processing of simultaneous spatially sampled signal, measuring a wavefront impinging from DOA $\theta$}
    \label{fig_ULA_imping}
\end{figure}
In complimentary to Fig.~\ref{fig_ULA_sketch}, Fig.~\ref{fig_ULA_imping} adds the processor layer of the beamformer.
\par A temporal snapshot measured by the array at time $t$ is
\begin{equation}
\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T},
\end{equation}
where $p_{n}$ denotes the $n$-th sensor position, $t$ denotes the continuous-time variable and $^{T}$ denotes the transpose operation. 
Considering the \emph{conventional beamformer} \cite{van2004optimum}, the output ($z\rBrace{t}$) is expressed by:
\begin{equation}
z\rBrace{t} = \sum_{n=0}^{N-1}{f\rBrace{t,p_{n}}\omega_{n}^{*}},
\end{equation}
where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at temporal frequency $\omega$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the direction of arrival (DOA) angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
The wave signal, spatially sampled by the sensor array inputs is
\begin{equation}
\label{eq_prlm_timeSpace_outputVec}
\vecnot{f}\rBrace{t,x} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
\end{equation}
where $\tau = \frac{d\cdot{}\cos{\theta}}{c}$ is the propagation delay between consecutive sensors and $c$ is the wave's velocity in the medium.
Considering narrowband signals, the time delay $\tau$ translates to a mere phase shift and the \emph{steering vector} takes the form of
\begin{equation}
\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\omega\tau\rBrace{N-1}}}^{T}.
\end{equation}
As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal sub space in the noiseless scenario.

### 2021-02-15 Modules/sec_rangeSensitivityError.tex
rev03

First, we notice that although setting $r\to1$ (i.e., close to perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks. 
Next, as evident from \eqref{eq_generalH}, the range error related sensitivity is $2\pi$-periodic with respect to $\dPhi$ (see Fig.~\ref{fig_hDUDTContour_mutliPeak}).

>>>>

First, we notice that although setting $r\to1$ (i.e., close to a perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks. 
Next, as evident from \eqref{eq_narmalized_pattern}, the range error related sensitivity is $2\pi$-periodic with respect to $\dPhi$ (see Fig.~\ref{fig_hDUDTContour_mutliPeak}).

### 2021-02-15 Modules/sec_stability.tex
rev03

In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms which are then used to define some basic simulation scenarios that will be thoroughly investigated throughout this chapter.  

@@

\subsection{Error terms}
In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
introducing the estimated steering vector 
\begin{equation}\label{eq:d_hat}
\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
\begin{equation}\label{eq:SF_CB}
            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
where \[
\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
is the normalized Dirichlet kernel and
\dTheta\triangleq\theta-\hat{\theta},\ \dPhi\triangleq\phi-\hat{\phi},\ 
r\triangleq g/\hat{g},
are defined as the DOA, range and gain error terms respectively.
\subsection{Temporal Simulations}

@@

Interestingly, the system's response of \eqref{eqn:GeneralFeedbackTransferFunction} is not frequency dependent, for it is exclusively governed by spatial parameters.
Therefore, in the absence of any previous related work on spatial feedback, we find that the commonly used Bounded-Input-Bounded-Output (BIBO) stability is appropriate. 
As such, assuming the \emph{Perfect alignment} scenario, we identify $r$ in \eqref{eq:SF_CB} to be the most influential for determining the system's stability for it controls the response's denominator - e.g. for $r<1$ the denominator will never be nullified.
As anticipated from \eqref{eq:SF_CB} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude does not converge to a finite value.
Also noticeable is the increase in the final amplitude value as $r$ increases.
In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value with respect to $r$ and find that the increase is substantial as $r$ increases towards 1.

@@

            \put (46, -5){\rotatebox{0}{$t/2\tau_{pd}$}}

@@

    The horizontal axis ($t/2\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.

@@

In each iteration the spatial focusing is increased, together with the received amplitude, as can be seen in Fig.~\ref{fig_beamThinning}.
The reader may notice that the $t=1\cdot{}\tau_{pd}$ plot is actually the conventional beampattern, for the feedback signal has not yet reimpinged the array.

@@

    We set $r=0.9$ and plot the beampattern for various simulation times.

@@

    For each $r$ (the horizontal axis), we plot the final received amplitude in dB.

@@

Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:futureResearch}.

@@

            \put (-3, 35){\rotatebox{90}{$t/2\tau_{pd}$}}

@@

    The plotted time is also normalized as in Fig.\ref{fig_stability}.

@@

Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e. the settling time remains the same as $N$ increases.

>>>>

In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms.
Using those error terms, some basic simulation scenarios are defined, raging from ideal to fully noised cases, which enable rigorous presentation of our findings.

@@

\subsection{Gain mismatch}

@@

% Interestingly, the system's response of \eqref{eqn:GeneralFeedbackTransferFunction} is not frequency dependent, for it is exclusively governed by spatial parameters.
% Therefore, 
In the absence of any previous related work on spatial feedback, we find that the commonly used Bounded-Input-Bounded-Output (BIBO) stability is appropriate. 
% As such, assuming the \emph{Perfect alignment} scenario, we identify $r$ in \eqref{eq:SF_CB} to be the most influential for determining the system's stability for it controls the response's denominator - e.g. for $r<1$ the denominator will never be nullified.
To this end, the gain mismatch
\begin{equation}
    r=g/\hat{g}
and plug \eqref{eq:alpha_beta_opt} into \eqref{eqn:GeneralFeedbackTransferFunction}, giving rise to
\begin{equation}\label{eq:SF_CB_gainMismatch}
            H_{\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}}
            = &\frac{
            g\vecnot{\beta}_{\text{CB,opt}}^{H}\vecnot{d}\exp{\rBrace{-j\phi}}
            }{
            1 - g\vecnot{\alpha}_{\text{CB,opt}}^{H}\vecnot{d}\exp{\rBrace{-j\phi}}
            }\\
            = &\frac{    
            \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
            }{
            1 - \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
            }\\
            = & \frac{r}{1-r}.
As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.
In Fig.~\ref{fig_stabilityVal}, we plot the final amplitude value after 100 iterations of the signal being retransmitted between the array and the target of interest and find that the final values substantially increase as $r\to{1}$.

@@

            \put (46, -5){\rotatebox{0}{$t/\tau_{pd}$}}

@@

    The horizontal axis ($t/\tau_{pd}$) is the time, normalized to the signal's round-trip duration to the target and back.

@@

In each iteration the mainlobe sharpens, as can be seen in Fig.~\ref{fig_beamThinning}.
The reader may notice in Fig.~\ref{fig_beamThinning} that the $t=1\cdot{}\tau_{pd}$ plot is actually the conventional beampattern, for the feedback signal has not yet re-impinged the array.

@@

    Simulation of same setup as in Fig.\ref{fig_stability} with $r=9$.
    Several simulations are conducted, where each is simulated with different duration.
    It actually illustrates the forming of the final beampattern in time as our analysis assumes infinite duration. 

@@

    After simulating same setup of Fig.\ref{fig_stability} for a fined grid of $r$, we plot the final received amplitude in dB with respect to $r$.

@@

Although outside of this work's scope, this issue will obviously be of great importance when considering dynamic targets, as will be discussed in the ``future research`` part of the concluding Chapter.~\ref{chap:conclusion}.

@@

            \put (-3, 35){\rotatebox{90}{$t/\tau_{\text{pd}}$}}

@@

    The plotted time is also in units of $\tau_{\text{pd}}$ normalized as in Fig.\ref{fig_stability}.

@@

Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB_gainMismatch} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e. the settling time remains the same as $N$ increases.
\subsection{Phase mismatch}
Using the same weights $\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}$, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
As we intend to compare the results to \cite{van2004optimum}, we consider a ULA, introducing its estimated steering vector
\begin{equation}\label{eq_est_d_ULA}
\hat{\vecnot{d}} = \vBrace{1, \exp{\rBrace{-\hat{\theta}}}, \hdots, \exp{\rBrace{-\rBrace{N-1}\hat{\theta}}}}^{T}.
Observing that
\begin{equation*}
        \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \vecnot{d}^{H}\hat{\vecnot{d}}\\
        =&\ \sum_{n=0}^{N-1}\exp{\rBrace{jn\Delta\theta}} \\
        =&\ \frac{\exp{\rBrace{jN\Delta\theta}}-1}{\exp{\rBrace{j\Delta\theta}}-1}\\
        =&\ \frac{\exp{\rBrace{jN\Delta\theta/2}}}{\exp{\rBrace{j\Delta\theta/2}}}\cdot
        \frac{\exp{\rBrace{jN\Delta\theta/2}}-\exp{\rBrace{-jN\Delta\theta/2}}}
        {\exp{\rBrace{j\Delta\theta/2}}-\exp{\rBrace{-j\Delta\theta/2}}}\\
        =&\ \exp{\rBrace{j\rBrace{N-1}\Delta\theta/2}}\cdot
        \frac{\sin{\rBrace{N\Delta\theta/2}}}
        {\sin{\rBrace{\Delta\theta/2}}},
\end{equation*}
we define Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernel}) as
D_{\test{orig}}\rBrace{x,N}\triangleq\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
and the normalized Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernelNorm})
\D{x}{N}=\frac{1}{N}D_{\test{orig}}\rBrace{x,N}=\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}.
Now, \eqref{eqn:GeneralFeedbackTransferFunction} takes the form of
        H_{\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}}
        = &\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}.
        \begin{overpic}[width=0.65\linewidth, 
        tics=10,trim=0 0 0 0]{./Media/DirichletKernels.png}
            \put (3, 26){\rotatebox{90}{$D_{\test{orig}}\rBrace{x,N}$}}
            \put (91, 32){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,2}$}}}
            \put (91, 53){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,5}$}}}
            \put (91, 59){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,7}$}}}
            \put (91, 8){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,10}$}}}
            \put (50, 2.5){\rotatebox{0}{$x$}}
            \put (12, 5){\rotatebox{0}{$-\pi$}}
            \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
            \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
            \put (89, 5){\rotatebox{0}{$\pi$}}
    Few illustrations of the Dirichlet kernel, for $N$ values of 2,5,7 and 10.
    \label{fig_DirichletKernel}
        \begin{overpic}[width=0.65\linewidth, 
        tics=10,trim=0 0 0 0]{./Media/DirichletKernelsNorm.png}
            \put (3, 32){\rotatebox{90}{$D\rBrace{x,N}$}}
            \put (86.5, 47){\rotatebox{80}{\tiny{$D\rBrace{x,7}$}}}
            \put (81.5, 47){\rotatebox{80}{\tiny{$D\rBrace{x,5}$}}}
            \put (84.5, 30){\rotatebox{-86}{\tiny{$D\rBrace{x,10}$}}}
            \put (75.5, 30){\rotatebox{-70}{\tiny{$D\rBrace{x,2}$}}}
            \put (50, 2.5){\rotatebox{0}{$x$}}
            \put (12, 5){\rotatebox{0}{$-\pi$}}
            \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
            \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
            \put (89, 5){\rotatebox{0}{$\pi$}}
    Few illustrations of the normalized Dirichlet kernel, for $N$ values of 2,5,7 and 10.
    \label{fig_DirichletKernelNorm}

### 2021-02-15 Modules/stabilityEnhancement_freqPairApproach.tex
rev03

As demonstrated in the previous section, the beampattern \eqref{eq_generalH} is sensitive to range errors.
We now propose an architecture which obtains the desired beampattern $\Hr_{\Delta\theta,\Delta\phi\to0,r}$ even for relatively large range errors $\Delta R_{\text{rt}}$. Also, we show that the suggested architecture achieves high performance at moderately low signal-to-noise ratio (SNR) scenarios.

\subsection{Intuition}
Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_generalH} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies. 
Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
Following the thorough spectrum use overview in \cite{barclay2003propagation}, among the notable considerations for choosing frequency in localization related schemes are
\begin{itemize}
    \item \textbf{Propagation efficiency}\\
    Due to the chemical structure of the atmosphere, some frequencies are propagated efficiently while other are absorbed \cite{wen2015foundations} by the atmosphere layers, being unsuitable for localization applications such as RADAR.
    \item \textbf{Antenna length}\\
    As described in \cite{barclay2003propagation}, although low ($<30_{\text{Khz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
    \item \textbf{Signal bandwidth}\\
    As the carrier signal's frequency decreases, so does the available bandwidth due to aliasing.
\end{itemize}
Henceforth, inspired by known trigonometrical identities where mathematical of two harmonics produces new frequencies which are the sum (or subtraction) of the original signals, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies. 
In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved.

@@

Note that in the suggested architecture we do not add array elements, but merely double the beamformer processing effort. 
\par For each FB block, its output is given by
\[
z_{i}(t)=H_{\vBetaI{i},\vAlphaI{i}}\rBrace{\omega_{i}}\exp{\rBrace{j\omega_{i}t}}\ \ {i\in\cBrace{1,2}},
\]
where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}'s RHS, we compute the reciprocal of each frequency response, average, and compute the reciprocal again. This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
\begin{equation}
    \label{eqn_HDF_def}
    Z_{\text{DF}} = \abs{H^{-1}_{\vBetaI{1}\vAlphaI{1}}\rBrace{\omega_{1}}+H^{-1}_{\vBetaI{2},\vAlphaI{2}}\rBrace{\omega_{2}}}^{-1}.
\end{equation}
% Note that, as in IIR filters, the system stabilizes after a certain period, therefore the Fourier weights should be calculated after stabilization.
% As a rule of thumb, simulations show that the stabilization period is around $100R/c$. 
For convenience, we use subscripts instead of formal $\omega$ dependency such that $\phiI{i}\triangleq\phi\rBrace{\omega_{i}}, \gI{i}\triangleq{}g\rBrace{\omega_{i}}, \vdI{i}\triangleq\vecnot{d}\rBrace{\omega_{i}}$.
Also, $r_i\triangleq{}\gI{i}/\gIHat{i}$ is denoted to be the gain mismatch at $\omega_i$.

@@

With this choice, and similarly to \eqref{eq:SF_CB}, \eqref{eqn_H_DF_general} becomes

>>>>

As demonstrated in the previous section, the beampattern \eqref{eq_narmalized_pattern} is sensitive to range errors.
We now propose an architecture which obtains the desired beampattern $\Hr_{\Delta\theta,\Delta\phi\to0,r}$ even for relatively large range errors $\Delta R_{\text{rt}}$. Also, we show that the suggested architecture achieves high performance at moderately low signal-to-noise ratio (SNR) scenarios.

\subsection{Intuition}
Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_narmalized_pattern} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies. 
Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
Following the thorough spectrum use overview in \cite{barclay2003propagation}, among the notable considerations for choosing frequency in localization related schemes are
\begin{itemize}
    \item \textbf{Propagation efficiency}\\
    Due to the chemical structure of the atmosphere, some frequencies are propagated efficiently while other are absorbed \cite{wen2015foundations} by the atmosphere layers, being unsuitable for localization applications such as RADAR.
    \item \textbf{Antenna length}\\
    As described in \cite{barclay2003propagation}, although low ($<30_{\text{KHz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength is large ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
    \item \textbf{Signal bandwidth}\\
    As the carrier signal's frequency decreases, so does the available bandwidth due to aliasing.
\end{itemize}
Henceforth, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies. 
In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved  as it will depend on the frequency difference $\omega_{1}-\omega_{2}$.

@@

Note that in the suggested architecture we do not add array elements, but merely double the beamformer processing effort. 
\par For each FB block, its output is given by
\[
z_{i}(t)=H_{\vBetaI{i},\vAlphaI{i}}\rBrace{\omega_{i}}\exp{\rBrace{j\omega_{i}t}}\ \ {i\in\cBrace{1,2}},
\]
where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_narmalized_pattern}'s RHS, we compute the reciprocal of each frequency response, average, and compute the reciprocal again. This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
\begin{equation}
    \label{eqn_HDF_def}
    Z_{\text{DF}} = \abs{H^{-1}_{\vBetaI{1}\vAlphaI{1}}\rBrace{\omega_{1}}+H^{-1}_{\vBetaI{2},\vAlphaI{2}}\rBrace{\omega_{2}}}^{-1}.
\end{equation}
% Note that, as in IIR filters, the system stabilizes after a certain period, therefore the Fourier weights should be calculated after stabilization.
% As a rule of thumb, simulations show that the stabilization period is around $100R/c$. 
For convenience, we use subscripts instead of formal $\omega$ dependency such that $\phiI{i}\triangleq\phi\rBrace{\omega_{i}}, \gI{i}\triangleq{}g\rBrace{\omega_{i}}, \vdI{i}\triangleq\vecnot{d}\rBrace{\omega_{i}}$.
Also, $r_i\triangleq{}\gI{i}/\gIHat{i}$ is denoted to be the gain mismatch at $\omega_i$.

@@

With this choice, and similarly to \eqref{eq_narmalized_pattern}, \eqref{eqn_H_DF_general} becomes

### 2021-02-15 front/abbrevs.tex
rev03

\abbreviationsAndNotation{
\begin{tabular}{p{2cm}@{:\quad}l}
QED & quod erat demonstratum \\
$c$ & the speed of light \\
$a\pm b$ & the closed interval $\left[a-b,a+b\right]$ \\
\end{tabular}
}

>>>>

\abbreviationsAndNotation{
\begin{longtable}{p{2cm}@{:\quad}l}
DOA & Direction of arrival \\
RADAR & RAdio Detection And Ranging \\
FIR & Finite impulse response \\
IIR & Infinite impulse response \\
ULA & Uniform linear array \\
FIM & Fisher information matrix \\
SNR & Signal to noise ratio \\
MUSIC & Multiple signal classification (algorithm)\\
RHS & Right hand side \\
FB & Feedback beamformer \\
SF & Single frequency \\
DF & Dual frequency \\
HPBW & Half power beamwidth \\
PDF & Probability density function \\
CRLB & Cram\'er Rao lower bound \\
CRB & Cram\'er Rao bound \\
PCA & Principal component analysis \\
ICA & Independent components analysis \\
MVDR & Minimum Variance Distortionless Response \\
UWB & Ultra wide band \\
HOS & High order statistics \\
$\vecnot{v}$ & A vector \\
$v_{i}$ & The $i$-th element of vector $\vecnot{v}$ \\
$\vecnot{v}^{T}$ & Transpose of vector $\vecnot{v}$ \\
$\vecnot{v}^{*}$ & Conjugate of vector $\vecnot{v}$ \\
$\vecnot{v}^{H}$ & Hermitian (conjugated) transpose of vector $\vecnot{v}$ \\
$\vecnot{A}$ & A Matrix \\
$A_{i,j}$ & The $i,j$-th element of matrix $\vecnot{A}$ \\
$\vecnot{A}^{T}$ & Transpose of matrix $\vecnot{A}$ \\
$\vecnot{A}^{*}$ & Conjugate of matrix $\vecnot{A}$ \\
$\vecnot{A}^{H}$ & Hermitian (conjugated) transpose of matrix $\vecnot{A}$ \\
$d$ & Array's inter-element spacing \\
$\omega$ & Radial frequency \\
$c$ & Wave's propagation velocity \\
$\lambda$ & Wavelength \\
$\theta_{d}$ & Geometrical angle \\
$\theta$ & Electrical phase \\
\vecnot{d} & Steering vector \\
$B$ & beampattern \\
$R$ & Distance to target \\
$z\rBrace{t}$ & Array's temporal output \\
$Z\rBrace{\omega}$ & Array's frequency-domain output \\
$\mathcal{D}$ & Directivity \\
$\mathcal{H}$ & Normalized beampattern \\
\end{longtable}
}

### 2021-02-15 main/chap_futureResearch.tex
Sent as draft No.2
rev03

In the following chapter, some of the many possibilities for further investigation of the feedback beamformer are suggested.
As mentioned in Sec.~\ref{sec:setup}, we assumed a single target stationary scenario where the target's location is fixed.
Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios which obviously should be followed by a combined general scenario of multiple dynamic targets performance scenario.
Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and it's affect on the overall spatial performance.
We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 
\section{Dynamic target}
\label{sec_future_dynamic}
\input{Modules/sec_future_dynamic}
\section{Multi-target scenario}
\label{sec_future_multiTarget}
\input{Modules/sec_future_multiTarget}
\section{Waveform modifications}
\label{sec_future_wavfrom}
\input{Modules/sec_future_wavfrom}
\section{Coefficients quality criteria}
\label{sec_future_coef}
\input{Modules/sec_future_coef}
% \section{Apply to other applications}
% \label{sec_future_applications}
% \input{Modules/sec_future_applications}

>>>>

In the following chapter, some of the many possibilities for further investigation of the feedback beamformer are suggested.
As mentioned in Sec.~\ref{sec_introduceFeedback}, we assumed a single stationary target scenario where the target's location is fixed.
Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios.
Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and it's affect on the overall spatial performance.
We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 
\subsection{Dynamic target}
\label{sec_future_dynamic}
\input{Modules/sec_future_dynamic}
\subsection{Multi-target scenario}
\label{sec_future_multiTarget}
\input{Modules/sec_future_multiTarget}
\subsection{Waveform modifications}
\label{sec_future_wavfrom}
\input{Modules/sec_future_wavfrom}
\subsection{Coefficients quality criteria}
\label{sec_future_coef}
\input{Modules/sec_future_coef}
% \section{Apply to other applications}
% \label{sec_future_applications}
% \input{Modules/sec_future_applications}
